Ownership types in theory and practice (in Rust)

### 2023-01-26 slides/slides.tex
Removed functional requirements line
Added borrow checker rules extra slide

\begin{frame}{Owners-as-modifiers: implications}
\begin{itemize}
  \item owners-as-modifiers: only the owners can modify objects
  \item model allows references to objects in arbitrary contexts, but restricts \emph{how} the references can be used
  \item fulfills requirements for verification of the functional correctness of object-oriented programs
\end{itemize}

@@

\begin{frame}{Conclusions and outlook}
\begin{itemize}
  % \item programming languages based on ownership types can eliminate many aliasing-related issues by enforcing strict rules on the existence and behavior of references to values
  \item \emph{owners-as-dominators} and \emph{owners-as-modifiers} models: different strictness on \emph{where} and \emph{how} references may be used
  \item Rust: 
  \begin{itemize}
    \item ownership-related rules that are strictly enforced at compile time
    \item helpful compile-time error messages instead of crashes or UB at runtime
    % \item omitting the need for many manual, rigorous and error-prone memory reference checks that programmers used to have to perform
    \item "fighting against the borrow checker" forces more explicit memory managenemt through ownership
  \end{itemize}
  \item will ownership types be incorporated into more new or existing programming languages in the future?
  \item maybe upcoming presentations on C++ enhancements (Carbon and cppfront) fix some of these issues?
\end{itemize}
\end{frame}

@@

>>>>

\begin{frame}{Owners-as-modifiers: implications}
\begin{itemize}
  \item owners-as-modifiers: only the owners can modify objects
  \item model allows references to objects in arbitrary contexts, but restricts \emph{how} the references can be used
  % \item fulfills requirements for verification of the functional correctness of object-oriented programs
\end{itemize}

@@

\begin{frame}{Conclusions and outlook}
\begin{itemize}
  % \item programming languages based on ownership types can eliminate many aliasing-related issues by enforcing strict rules on the existence and behavior of references to values
  \item \emph{owners-as-dominators} and \emph{owners-as-modifiers} models: different strictness on \emph{where} and \emph{how} references may be used
  \item Rust: 
  \begin{itemize}
    \item ownership-related rules that are strictly enforced at compile time
    \item helpful compile-time error messages instead of crashes or UB at runtime
    % \item omitting the need for many manual, rigorous and error-prone memory reference checks that programmers used to have to perform
    % \item "fighting against the borrow checker" forces more explicit memory managenemt through ownership
  \end{itemize}
  \item will ownership types be incorporated into more new or existing programming languages in the future?
  \item maybe upcoming presentations on C++ enhancements (Carbon and cppfront) fix some of these issues?
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Borrow-checker rules}
  program is valid if all of the below hold for all references:
  \begin{enumerate}
    \item the reference can only be used while its lifetime is ongoing
    \item the original referent is not used at all (for mutable references) or does not get mutated (for immutable references) until the lifetime of the newly created reference has expired.
  \end{enumerate}
\end{frame}
